---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data <- read.csv(unz("activity.zip", "activity.csv"), header=TRUE, sep=",",  quote="\"", na.strings="NA")
data$date <- as.Date(data$date, format="%Y-%m-%d")
```

## What is mean total number of steps taken per day?
* Calculate the total number of steps taken per day
```{r}
total <- aggregate(data$steps, by=list(data$date), FUN=sum)
names(total) <- c("date", "totalsteps")
```
* Make a histogram of the total number of steps taken each day
```{r}
hist(total$totalsteps, xlab="Total Steps Per Day", main="Histogram of Total Steps Per Day")
```

* Calculate and report the mean and median of the total number of steps taken per day
```{r}
stepsmean <- mean(total$totalsteps, na.rm=TRUE)
stepsmedian <- median(total$totalsteps, na.rm=TRUE)
```
+ Mean: `r stepsmean`
+ Median: `r stepsmedian`

## What is the average daily activity pattern?
* Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
daily <- aggregate(data$steps, by=list(data$interval), FUN=mean, na.rm=TRUE)
names(daily) <- c("interval", "meansteps")
plot(y=daily$meansteps, x=daily$interval, type="l", xlab="Interval", ylab="Average Steps")
```

* Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps
```{r}
maxrow <- daily[daily$meansteps == max(daily$meansteps), ]
interval <- maxrow$interval
```
+ Interval: `r interval`

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
