---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data <- read.csv(unz("activity.zip", "activity.csv"), header=TRUE, sep=",",  quote="\"", na.strings="NA")
data$date <- as.Date(data$date, format="%Y-%m-%d")
```

## What is mean total number of steps taken per day?
* Calculate the total number of steps taken per day
```{r}
total <- aggregate(data$steps, by=list(data$date), FUN=sum)
names(total) <- c("date", "totalsteps")
```
* Make a histogram of the total number of steps taken each day
```{r}
hist(total$totalsteps, xlab="Total Steps Per Day", main="Histogram of Total Steps Per Day")
```

* Calculate and report the mean and median of the total number of steps taken per day
```{r}
stepsmean <- mean(total$totalsteps, na.rm=TRUE)
stepsmedian <- median(total$totalsteps, na.rm=TRUE)
```
+ Mean: `r stepsmean`
+ Median: `r stepsmedian`

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
